

\documentclass[12pt,letterpaper,roman]{moderncv}      
\usepackage[english]{babel}



\moderncvstyle{classic}                            
\moderncvcolor{green}                            

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Omid}{Karimpour}
\address{596 Haines Road}{Newmarket, Ontario}{Canada}
\phone[mobile]{(647) 447-5915}               
\email{okarimpour@gmail.com}                             
\homepage{http://omidkarimpour.ca}  

\begin{document}

\recipient{To}{}
\date{\today}
\opening{To whom may concern,}
\closing{Best regards,}
\makelettertitle

Please accept the accompanying resume as an application for the position of “". I am a Robotics Researcher and an Adjunct Faculty of the School of Trades and Technology at Fleming College. I have experiences in research, teaching, mentorship, project management, and management in my portfolio. Besides that, I am extremely passionate about robotics and problem-solving. In these moments, most of the times I find myself wearing different hats and get involved in various projects. 

My background is diverse in Electronics, Hardware, Software, Machine Learning and Robotics. Most of my works are focused on solving the navigation side of autonomous robots’ challenges and satisfying my hunger to find more. As Richard Feynman said, “I am smart enough to know that I am dumb”. With this mindset, I am interested in solving planning problems in any sense from artificial intelligence and robotics solutions to pure control. 

I would love to explore your culture, know more about the responsibilities and discuss my qualifications. Please feel free to check my \href{http://omidkarimpour.ca}{Website: http://omidkarimpour.ca} and contact me at \href{mailto:okarimpour@ieee.org}{okarimpour@ieee.org} with any further inquiries.

\vspace{0.5cm}


\makeletterclosing

\end{document}
