%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academy Membership}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {IEEE (Institute of Electrical \& Electronics Engineers)} % Organization/group
    {Ryerson Student Branch} % Location
    {Nov. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Organized a project showcase for faculties, graduates, and undergraduates}
        \item {Hosted an "Improving Communications Skills for Engineers" workshop}
        \item {Participated and started several IEEE events such as Industry Night}
      \end{cvitems}
    }

%---------------------------------------------------------
\iffalse
 \cventry
    {Member} % Affiliation/role
    {Hardware-software co-design, DE2-Altera FPGA based, and Nios II SoPC Development} % Organization/group
    {Embeded System} % Location
    {Sep. 2017 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Real-time scheduling techniques, concurrency, system on chip and hardware software codesign tools}
        \item {Real-time scheduling and investigating RTOS using uVision, RTX, and ARM Cortex M3}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {Reliability evaluation \& build in self repair of reconfigurable} % Organization/group
    {Digital System Testing} % Location
    {Jan. 2017 - June. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Reliability analysis \& comparison of hierarchical redundancy, optimal repair, coarse redundancy, Tile-based}
        \item {Analyzed combinational and sequential circuit test generation methods. memory, delay testing, and testability design methodology}
      \end{cvitems}
    }
    
%--------------------------------------------------------- 
 \cventry
    {Core Member} % Affiliation/role
    {Architecture analysis and high-level synthesis of ASP of a VOP buffer} % Organization/group
    {Architiectural Synthesis} % Location
    {Sep. 2012 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Analyze the fully pipelined variant of architecture to get the highest performance of ASP along with 32-bit Multi Cycle Processor design.}
        \item {Assess the economic aspects, power consumption, and VOP area, determined by the available memory
			bandwidth}
      \end{cvitems}
    }
\fi
%---------------------------------------------------------
\end{cventries}
