%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

 %---------------------------------------------------------
  \cventry
    {Fleming College} % Job title
    {Adjunct Faculty} % Organization
    {Peterborough, ON} % Location
    {Jan. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Mechatronics Course Developer, design the course materials including lectures, labs, exams \& projects
            \begin{itemize}
                \item Hardware design for the labs and projects utilizing various sensors, DC, Servo and stepper motor controls.
                \item Software design for path planning, robot control systems and hybrid systems
            \end{itemize}
        \item Lead Instructor and Mentor of Applied Projects and Student Capstones
            \begin{itemize}
        		\item Student performance development through lab sections in Electronics \& Electricity labs
        		\item Utilizing Agile Project Management to meet sponsors desired expectations within the scope of agreements
        		\\*
            \end{itemize}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Network Centric Applied Research Team} % Job title
    {Robotics Researcher} % Organization
    {Toronto, ON} % Location
    {Aug. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Developing and implementing a modified Pioneer 2DX Autonomous Mobile Robot using RPLidar, localization, SLAM, mapping, path planning, and obstacle avoidance
        \begin{itemize}
        		\item Comparison of Gmapping, EKF, Hector, SLAM systems
        		\item Premapping and SLAM in Search \& Rescue Field research
        		\item Stair mapping, glass detection, and navigation, investigation
        		\\
        \end{itemize}
      \end{cvitems}
    }
 %---------------------------------------------------------
  \cventry
    {SDI Marketing (TMS)} % Job title
    {Manager \& Lead Advisor} % Organization
    {Newmarket, ON} % Location
    {Sep. 2015 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Managed and oversaw the operations of multiple stores. Developed and performed incentives, and trained District’s employees \& lead advisors
        \begin{itemize}
        		\item Multiple award winner for top sale performance
        		\item Generated a 314\% growth in revenue (Over \$1M Revenue)
        		\item Earned a reputation for effective leadership under ambitious deadlines
        		\\*
        \end{itemize}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \iffalse
  \cventry
    {McMaster University} % Job title
    {Research Participant} % Organization
    {Hamilton, ON} % Location
    {Jan. 2016 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Worked with \textbf{Prof. Jamal Deen} to analyze gait kinematics and gait kinetics. This led to a survey on Smart Joint Methods utilizing gyroscopes, force plates, EMG, \& muscle force. Further investigated the Slavelberg, Former-Cordero estimate of 3D ground reaction forces (GRFs), and optimal placement of accelerometers.	
        \begin{itemize}
        		\item Gait analysis, accuracy and reliability of Smart Joint Methods and Optimal Sensors Placement
        		\item  Surveyed the Bro, Intille and Gjoreski approaches based on accelerators, gyroscopes, and force sensors
        \end{itemize}
      \end{cvitems}
    }
    \fi

\end{cventries}
